Near infrared spectrum of a Class 0 protostar photosphere

### 2017-05-30 document/ms.tex
Update MS includes info on SMM1

@@

\begin{tabular}{lp{3cm}rrr}
\hline
\multicolumn{4}{c}{Marginal PDF} \\
\cline{3-5}
Parameter & Description & $|_{16\%}$& Median & $|_{84\%}$ \\
\hline
$\teff$   & Stellar effective temperature  (K) &   3000 & 3200 & 3600  \\
$\logg$   & Surface gravity & 2 & 3 & 4 \\
$\Z$   & Metallicity & - & - & - \\
$v_r$   & Velocity error & - & - & - \\
$\epsilon$   & Resolution error & - & - & - \\
$\Omega_\star/\Omega_d$   & Star/Disk solid angle ratio  & - & - & - \\
$\hat r_K$   & Estimated $K-$band veiling  & - & - & - \\
$T_d$   & Black body disk temperature & - & - & - \\
$A_K$   & $K-$band extinction & - & - & - \\
$\alpha$   & Exponent of reddening law & - & - & - \\
$a_{\rm G}$   & GP covariance kernel amplitude & - & - & - \\
$\ell$   & GP covariance kernel scale length & - & - & - \\
\hline
\end{tabular}

>>>>

\subsection{SMM1}
We also performed spectral inference on the source SMM1, a less embedded protostar showing less-conspicuous CO lines in its NIRSPEC $K-$band spectrum.  The conditions of the inference we identical to those of S68N, namely the same stellar and nuissance parameter ranges and priors.  We ran the MCMC sampling for a total of 20000 steps, discarding the first 15000 as burn-in.  Figure \ref{fig:SMM1_spectrum} shows the spectrum of SMM1 with a model spectrum possessing parameters randomly chosen from its posterior samples.

\begin{figure}
 \centering
 \includegraphics[width=0.85\columnwidth]{figures/SMM1_spectrum.pdf}
 \caption{Observed and modeled spectrum of SMM1 with residual noise spectrum.}
 \label{fig:SMM1_spectrum}
\end{figure}

@@

\begin{tabular}{lp{3cm}rrr}
\hline
\multicolumn{4}{c}{Marginal PDF} \\
\cline{3-5}
Parameter & Description & $|_{16\%}$& Median & $|_{84\%}$ \\
\hline
$\teff$   & Stellar effective temperature  (K) &   3000 & 3200 & 3600  \\
$\logg$   & Surface gravity & 2 & 3 & 4 \\
$v_r$   & Velocity error & - & - & - \\
$\epsilon$   & Resolution error & - & - & - \\
$\Omega_\star/\Omega_d$   & Star/Disk solid angle ratio  & - & - & - \\
$\hat r_K$   & Estimated $K-$band veiling  & - & - & - \\
$T_d$   & Black body disk temperature & - & - & - \\
$A_K$   & $K-$band extinction & - & - & - \\
$\alpha$   & Exponent of reddening law & - & - & - \\
$a_{\rm G}$   & GP covariance kernel amplitude & - & - & - \\
$\ell$   & GP covariance kernel scale length & - & - & - \\
\hline
\end{tabular}
